Combining neural networks and geostatistics for landslide hazard assessment of San Salvador Metropolitan Area, El Salvador \newline \newline Combinando redes neuronales y geoestad\'{i}stica para evaluaci\'{o}n de deslizamientos de tierra de el \'{a}rea Metropolitana de San Salvador, El Salvador

### 2015-05-31 paper.tex
Update paper.tex
31 may 2015 9:30

\pagestyle{fancy}
\fancyhead{}
\fancyhead[RE]{\thepage \hfill {\sc r. ríos -- c.gámez }}
\fancyhead[LO]{{\sc combining neural networks and geostatistics for landslide hazard assessment of san salvador department, el salvador } \hfill \thepage}
\fancyfoot{}
\fancyfoot[RE]{{\scriptsize{\it Rev.Mate.Teor.Aplic.} (ISSN 1409-2433) {Vol. 19}(1): 1--10, January 2012}}
\fancyfoot[LO]{{\scriptsize{\it Rev.Mate.Teor.Aplic.} (ISSN 1409-2433) {Vol. 19}(1): 1--10, January 2012}}
\paginas{1}{10} % Numeros de página, la versión final la pone el editor; Page numbers, the Editor puts the final numbers
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphics}
\usepackage{graphicx} % En caso de usar figuras, con formato .esp; In case of using figures, with format .eps
\usepackage{float} 
\usepackage{url}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{authblk}

@@

\selectlanguage{spanish}
\title{Combining neural networks and geostatistics for landslide hazard assessment of San Salvador Department, El Salvador 
\newline
\newline
Combinando redes neuronales y geoestadística para evaluación de deslizamientos de tierra en San Salvador,Departamento de El Salvador}

\author[1]{Ricardo Ríos \thanks{ricardo.rios.sv@gmail.com}}
\author[2]{Carlos Gámez \thanks{gamez9e@yahoo.com}}
\affil[1]{Department of Mathematics, Science and Mathematics Faculty, University of El Salvador, El Salvador.}
\affil[2]{Department of Mathematics, Science and Mathematics Faculty, University of El Salvador, El Salvador.}

@@

\section{Brief State of Art}
\label{sec:brief}
Since the pioneering work (\cite{Carrara1983403}), several mathematics and statistics models have been proposed to model landslide susceptibility: deterministic models (\cite{hessd-10-12643-2013},  \cite{doi:10.1080/19475705.2010.498151} and \cite{Neu2012511}), probabilistic models (\cite{Bern198839}, \cite{Chung2003451} and \cite{doi:10.1080/01431160310001618734} )
%, fuzzy set theory (\citet{Kanungo2006347} and \citet{Guettouche20133163}) 
and neural networks (\cite{Melchiorre2011410},\cite{Zeng2001374} and \cite{Ermini2005327}).

There are two important applications of the neural network models to landslide susceptibility. The first (\cite{Yesilnacar2005251})

Despite of the recent use of maps in those published works have not given enough attention on the use of geostatistical models to interpolate spatially distributed landslide susceptibility just landslide susceptibility is given in the georeferenced points and showed in the map of susceptibility.

>>>>

\pagestyle{fancy}
\fancyhead{}
\fancyhead[RE]{\thepage \hfill {\sc r. ríos -- c.gámez }}
\fancyhead[LO]{{\sc Combining neural networks and geostatistics for landslide hazard assessment of San Salvador Metropolitan Area, El Salvador } \hfill \thepage}
\fancyfoot{}
\fancyfoot[RE]{{\scriptsize{\it Rev.Mate.Teor.Aplic.} (ISSN 1409-2433) {Vol. 19}(1): 1--10, January 2012}}
\fancyfoot[LO]{{\scriptsize{\it Rev.Mate.Teor.Aplic.} (ISSN 1409-2433) {Vol. 19}(1): 1--10, January 2012}}
\paginas{1}{10} % Numeros de página, la versión final la pone el editor; Page numbers, the Editor puts the final numbers
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphics}
\usepackage{graphicx} % En caso de usar figuras, con formato .esp; In case of using figures, with format .eps
\usepackage{float} 
\usepackage{url}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{authblk}

@@

\selectlanguage{spanish}
\title{Combining neural networks and geostatistics for landslide hazard assessment of San Salvador Metropolitan Area, El Salvador 
\newline
\newline
Combinando redes neuronales y geoestad\'{i}stica para evaluaci\'{o}n de deslizamientos de tierra de el \'{a}rea Metropolitana de San Salvador, El Salvador}

\author[1]{Alex Rib\'{o} \thanks{alexandre4rt@gmail.com }}
\author[2]{Giovanni Molina \thanks{giova.molina@gmail.com}}
\author[3]{Ricardo Ríos \thanks{ricardo.sv@gmail.com}}

\affil[1]{National Institute of Health, Ministry of Health of El Salvador, El Salvador.}
\affil[2]{Ministry of Environment and Natural Resources of El Salvador.}
\affil[3]{Department of Mathematics, Science and Mathematics Faculty, University of El Salvador, El Salvador.}

@@

\section{Brief State of Art}
\label{sec:brief}
Since the pioneering work (\cite{Carrara1983403}), several mathematics and statistics models have been proposed to model landslide susceptibility: deterministic models (\cite{hessd-10-12643-2013},  \cite{doi:10.1080/19475705.2010.498151} and \cite{Neu2012511}), probabilistic models (\cite{Bern198839}, \cite{Chung2003451} and \cite{doi:10.1080/01431160310001618734} ).

According to

Recently 
%, fuzzy set theory (\citet{Kanungo2006347} and \citet{Guettouche20133163}) 
and neural networks (\cite{Melchiorre2011410},\cite{Zeng2001374}, \cite{Ermini2005327}) and \cite{Yesilnacar2005251}.

%There are two important applications of the neural network models to landslide susceptibility. The first (\cite{Yesilnacar2005251})

%Despite of the recent use of maps in those published works have not given enough attention on the use of geostatistical models to interpolate spatially distributed landslide susceptibility just landslide susceptibility is given in the georeferenced points and showed in the map of susceptibility.
